Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-02-13 README.Rmd
month of reaction analysis done

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

> Francuzik et al. , (2019). _Insect Venom Anaphylaxis, observetional study of the European Anaphylaxis Registry_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _Title of paper_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Insect Venom Anaphylaxis, observetional study of the European Anaphylaxis Registry'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
Title <- "Case-control study of Insect Venom Anaphylaxis from the European Anaphylaxis Registry."
```

@@

> Francuzik et al., (2019).  Name of journal/book <https://doi.org/xxx/xxx>

@@

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_ Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

**Data :** [CC-BY-4.0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### 2019-02-13 analysis/paper/paper.Rmd
month of reaction analysis done

The European Anaphylaxis Registry [@Grabenhenrich2016] database from March 2018 wassearched for anaphylaxis cases elicited by insect venom. The flowchart in figure \@ref(fig:flowchart) represents the detailed case-selection process.

@@

<!-- ## Data handling and statisitcs -->
The statistical analysis was performed in the R Statistical Package [@R]. Simple comparison of categorical variables was performed using Fisher's exact test, continuous variables were analyzed using Mann-Whitney U test. We defined statistical significance as α = 0.05. Data along with the analysis script can be accessed at online at....

@@

```{r}
demoTab
```

```{r, results='asis'}
st_options('bootstrap.css', FALSE)
#rdb %>% select()
ctable(rdb$d_centres_country %>% sapply(function(x){
  as.character(x) %>% factor()
}), rdb$q_340_insects%>% sapply(function(x){
  as.character(x) %>% factor()
}), style = 'rmarkdown',
       useNA = "no",
       prop = "r",
       totals = F,
       round.digits = 1,
dnn = c("Countries","Insects"))

```
```{r}
plot.proportions(rdb, "d_centres_country","q_340_insects")

@@

```{r}
cdplot(grouping~d_age,data = rdb)
```

@@

```{r}
testInsectsbinomialTab$prophylaxis[,-7] %>% knitr::kable()
```

@@

>>>>

The European Anaphylaxis Registry [@Grabenhenrich2016] database from March 2018 was searched for anaphylaxis cases elicited by insect's venom. The flowchart in figure \@ref(fig:flowchart) represents the detailed case-selection process.

@@

<!-- ## Data handling and statisitcs -->
The statistical analysis was performed in the R Statistical Package [@R]. Simple comparison of categorical variables was performed using either Chi^2^ test or Fisher's exact test (where the number of observation in a bin was less then 10), continuous variables were analyzed using Mann-Whitney U test. We defined statistical significance as α = 0.05. Data along with the analysis script can be accessed at online at https://github.com/wolass/venomanaphylaxiscompendium.

@@

We saw a significant difference in the clinical features of insect anaphylaxis in children and adults. The younger popoulation significantly less often had concomitant conditions (i.e. DM, HT, malignant diseases and mastocytosis), and more often presented with atopic dermatitis, rhinitis and asthma. Therefore, we decided to analyse these groups separately.

```{r}
demoTab %>% rbind(demo_age_tab) %>% t() %>%  
  {data.frame(` `=rownames(.),.)} %>%
#   flextable(col_keys = c("X.","female","male","children.adolescents","adults")) 
# topology <- data.frame(col_keys = c("X.","female","male","children.adolescents","adults"),
#                        colB = c("","Sex","Sex","Age","Age"),
#                        ColA = c("","Female","Male","<18",">=18"))
# tempT %>%  
#   set_header_df(mapping = topology,key = "col_keys") %>% 
#   merge_h(part="header") %>% 
#   merge_v() %>% 
#   empty_blanks() %>% 
#   autofit()
knitr::kable(col.names = c("","female","male","<18","adults"),row.names = F)
```

```{r, results='asis'}
# st_options('bootstrap.css', FALSE)
# #rdb %>% select()
# ctable(rdb$d_centres_country %>% sapply(function(x){
#   as.character(x) %>% factor()
# }), rdb$q_340_insects%>% sapply(function(x){
#   as.character(x) %>% factor()
# }), style = 'rmarkdown',
#        useNA = "no",
#        prop = "r",
#        totals = F,
#        round.digits = 1,
# dnn = c("Countries","Insects"))

@@

```{r insectsgeo, fig.cap="Proportion of anaphylaxis cases elicited by specific insects in reporting countries. Less frequent insects were groupeped together as 'other'."}
plot.proportions(rdb, "d_centres_country","q_340_insects")
```

The Figure \@ref(fig:insectsgeo) shows the distribution of insects according to the geographic area (countries).

```{r}
plot_MOR
```

@@

@@

```{r reactionmonthincountries, fig.cap="Proportional insect venom induced anaphylaxis to specific insects during a year according to countries.", fig.height=8,fig.width=5}
plot_MOR+
  facet_grid(d_centres_country~.)
```

```{r}
plot_MOR
```
